Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-03-07 WRITEUP/ms.tex
Updates from Overleaf

\citestyle{aa}
\shorttitle{Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization
}
\shortauthors{Leung et al.}

\begin{document}
\title{
Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization
}

@@

\begin{abstract}
We study the dynamical properties of molecular clouds complexes (MC) in a prototypical galaxy (\flower)
and its satellite galaxies at the Epoch of Reionization (EoR) using cosmological zoom-in simulation.
We identify MCs using H$_2$ density, 
and compare their masses, sizes, velocity dispersions, gas surface densities, and virial parameters ($\alpha_{\rm vir}$)
with those observed in nearby and \z$\sim$\,2 galaxies.
The MCs span a mass range of $10^{6.5-9}$\,\Msun. Their velocity dispersions and gas surface densities are 
systematically higher than those observed in nearby galaxies, but comparable to starburst galaxies.
We compute the effective two-component Toomre $Q$ parameter (gas and stars) to examine 
regions that are unstable to local axisymmetric perturbations. 
We further perform virial analysis, which is accessible from observations, to examine regions likely 
to undergo collapse.
Our analysis indicates that the MCs in the main disk of \flower are unbound, but its 
substructures have lower virial parameters and Toomre $Q$, which is
consistent with the notion that collapsing structures occur within globally stable structures.
We find $\alpha_{\rm vir}\approx$\,2 for the MCs in the satellite galaxies,
which we interpret as result of the weaker stellar feedback and less frequent \SF compared to \flower.
Our results suggest that the more massive and bigger MCs compared to the Milky Way
manifest from the higher gas mass fraction, surface density, and velocity dispersion.
% , which together sets the scale for fragmentation.
High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the
Next Generation Very Large Array (ngVLA)
can furnish scrutinizing data to test our findings and shed light on \SF since the cosmic dark ages.
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

@@

%--------------------------------------------------------------------------
%                                Introduction
%--------------------------------------------------------------------------
\section{Introduction}    \label{sec:intro}

@@

To account for stabilizing effect of both gas and stars and the non-negligible disk thickness, 
% since thickness of a disk weakens the gravitational forces within the disk plane and lower the values for $Q$
% Romeo:  The effect of thickness is to increase the stability parameter of each 
% component by a factor T, which depends on the ratio of vertical to radial velocity dispersion, following eqn 8 of their paper.
we consider the approximation for the effective two-component $Q_{\rm eff}$ parameter following \citet{Romeo11a} and
\citet{Inoue16a} which is expressed as follows:
\begin{equation}
Q^{-1}_{\rm eff} = \[ \left\{
				\begin{array}{lccr}
					     {\displaystyle\frac{w}{T_{\rm star} Q_{\rm star}} + \frac{1}{T_{\rm gas} Q_{\rm gas}}}      & & & \mbox{if\ }T_{\rm star} Q_{\rm star} \geq T_{\rm gas} Q_{\rm gas} \\ [0.75em]
                                               {\displaystyle\frac{1}{T_{\rm star} Q_{\rm star}} + \frac{w}{T_{\rm gas} Q_{\rm gas}}}      & & & \mbox{if\ }T_{\rm star} Q_{\rm star} \leq T_{\rm gas} Q_{\rm gas} \\				
				\end{array} 
			    \right,
			    \]
\end{equation}
where $w$ is defined as:
\begin{equation}
w\equiv\frac{2 \sigma_{\rm star} \sigma_{\rm gas}}{\sigma_{\rm star}^2 + \sigma_{\rm gas}^2},
\end{equation}
and $T$ is approximated as:
\begin{equation}
T = \[ \left\{
		\begin{array}{lccr}
			{\displaystyle 0.8 + 0.7\left(\frac{\sigma_{z}}{\sigma_{r}}\right)}      && & \mbox{if\ } \sigma_z \lesssim 0.5 \times \sigma_r \\ [1.25em]
			{\displaystyle 1 + 0.6\left(\frac{\sigma_{z}}{\sigma_{r}}\right)}        & & & \mbox{if\ } \sigma_z \gtrsim 0.5 \times \sigma_r 
\\
		\end{array}
	\right \rlap{.}
	\]
\end{equation}

>>>>

\citestyle{aa}
\shorttitle{Dynamical Properties of MC in Galaxies at the EoR
}
\shortauthors{Leung et al.}

\begin{document}
\title{Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization}

@@

\begin{abstract}
We study the dynamical properties of molecular clouds complexes (MC) in a prototypical galaxy (\flower) and its satellite galaxies at the Epoch of Reionization (EoR) using cosmological zoom-in simulation.
%
We identify MCs using H$_2$ density, and compare their masses, sizes, velocity dispersions, gas surface densities, and virial parameters ($\alpha_{\rm vir}$) with those observed in nearby and \z$\sim$\,2 galaxies.
%
The MCs span a mass range of $10^{6.5-9}$\,\Msun. Their velocity dispersions and gas surface densities are systematically higher than those observed in nearby galaxies, but comparable to starburst galaxies.
%
We compute the effective two-component Toomre $Q$ parameter (gas and stars) to examine regions that are unstable to local axisymmetric perturbations. 
%
We further perform virial analysis, which is accessible from observations, to examine regions likely 
to undergo collapse. Our analysis indicates that the MCs in the main disk of \flower are unbound, but its substructures have lower virial parameters and Toomre $Q$, which is consistent with the notion that collapsing structures occur within globally stable structures.
%
We find $\alpha_{\rm vir}\approx$\,2 for the MCs in the satellite galaxies, which we interpret as result of the weaker stellar feedback and less frequent \SF compared to \flower. Our results suggest that the more massive and bigger MCs compared to the Milky Way manifest from the higher gas mass fraction, surface density, and velocity dispersion.
% , which together sets the scale for fragmentation.
High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the Next Generation Very Large Array (ngVLA) can furnish scrutinizing data to test our findings and shed light on \SF since the cosmic dark ages.
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

@@

%--------------------------------------------------------------------------
%                                Introduction
%--------------------------------------------------------------------------

\section{Introduction}\label{sec:intro}

@@

To account for stabilizing effect of both gas and stars and the non-negligible disk thickness, 
% since thickness of a disk weakens the gravitational forces within the disk plane and lower the values for $Q$
% Romeo:  The effect of thickness is to increase the stability parameter of each 
% component by a factor T, which depends on the ratio of vertical to radial velocity dispersion, following eqn 8 of their paper.
we consider the approximation for the effective two-component $Q_{\rm eff}$ parameter following \citet{Romeo11a} and
\citet{Inoue16a} which is expressed as follows:
\begin{equation}
Q^{-1}_{\rm eff} =  \left\{
				\begin{array}{lccr}
					     {\displaystyle\frac{w}{T_{\rm star} Q_{\rm star}} + \frac{1}{T_{\rm gas} Q_{\rm gas}}}      & & & \mbox{if\ }T_{\rm star} Q_{\rm star} \geq T_{\rm gas} Q_{\rm gas} \\ [0.75em]
                                               {\displaystyle\frac{1}{T_{\rm star} Q_{\rm star}} + \frac{w}{T_{\rm gas} Q_{\rm gas}}}      & & & \mbox{if\ }T_{\rm star} Q_{\rm star} \leq T_{\rm gas} Q_{\rm gas} \\				
				\end{array} 
			    \right.
\end{equation}
where $w$ is defined as:
\begin{equation}
w\equiv\frac{2 \sigma_{\rm star} \sigma_{\rm gas}}{\sigma_{\rm star}^2 + \sigma_{\rm gas}^2},
\end{equation}
and $T$ is approximated as:
\begin{equation}
T = \left\{
		\begin{array}{lccr}
			{\displaystyle 0.8 + 0.7\left(\frac{\sigma_{z}}{\sigma_{r}}\right)}      && & \mbox{if\ } \sigma_z \lesssim 0.5 \times \sigma_r \\ [1.25em]
			{\displaystyle 1 + 0.6\left(\frac{\sigma_{z}}{\sigma_{r}}\right)}        & & & \mbox{if\ } \sigma_z \gtrsim 0.5 \times \sigma_r 
\\
		\end{array}
	\right.
\end{equation}
